---
title: "p8105_hw1_yz4181"
author: Yuanyuan Zeng
output: html_document
---

# Question 1 

### Create a dataframe

```{r}
library(tidyverse)
```

```{r}
set.seed(1)

df = tibble(
  samp = rnorm(10),
  samp_logical = samp > 0,
  samp_character = nchar(samp),
  samp_levels = as.numeric(as.factor(samp_character))
)
```

### Calculate the mean of each variable in dataframe
```{r}
#calculate the mean of random size of 10
mean(pull(df, samp))

#calculate the mean of logical vector
logical_vector = pull(df, var = 2)
mean(logical_vector)

#calculate the mean of character vector
character_vector = pull(df, var = 3)
mean(character_vector)

#calculate the mean of factor vector
factor_vector = pull(df, var = -1)
mean(factor_vector)
```

# Problem 2
```{r}
data("penguins", package = "palmerpenguins")
skimr::skim(penguins)
mean(penguins$flipper_length_mm)
```

Description of dataset:
The dataset includes 344 rows and 8 columns. There are 2 factor vectors and 5 numeric vectors. The variables in the dataset are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. There are many missing value in column of sex, bill_length_mm, bill_depth_mm, flipper_length_mm, and  body_mass_g. 

###scatter plot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species))
```

