---
title: "p8105_hw1_yz4181"
author: Yuanyuan Zeng
output: html_document
---

## Problem 1 

#### Create a dataframe

```{r}
library(tidyverse)
```

```{r}
set.seed(1)

df = tibble(
  samp = rnorm(10),
  samp_logical = samp > 0,
  samp_character = c("Monday", "Tusday", "January", "October", "Saturday", "June", "Friday", "April", "March", "Sunday" ),
  samp_levels = factor(c("Fair", "Good", "Good", "Fair", "Excellent", "Fair", "Good", "Excellent", "Fair", "Excellent"))
)
```

#### Calculate the mean of each variable in dataframe
```{r}
#calculate the mean of random size of 10
mean(pull(df, var = 1))

#calculate the mean of logical vector
mean(pull(df, var = 2))

#calculate the mean of character vector
mean(pull(df, var = 3))

#calculate the mean of factor vector
mean(pull(df, var = -1))
```
The means of numeric vector and logical vector can be calculated. But the means of character vector and factor vector cannot be calculated.

#### Convert the variables from one to another
```{r}

```





## Problem 2

```{r}
# import the data set
data("penguins", package = "palmerpenguins")

# look at the data set
skimr::skim(penguins)

# Calculate mean flipper length
mean(penguins$flipper_length_mm)
```

Description of data set:
The data set includes 344 rows and 8 columns. There are 2 factor vectors and 5 numeric vectors. The variables in the data set are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. Some values are missing in column of sex, bill_length_mm, bill_depth_mm, flipper_length_mm, and  body_mass_g. 


```{r}
# make a scatterplot
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species))

# save the plot
ggsave("penguins.pdf")
```

