---
title: "p8105_hw1_yz4181"
author: Yuanyuan Zeng
---

## Problem 1 

#### Create a dataframe

```{r}
library(tidyverse)
```

```{r}
set.seed(1)

df = tibble(
  samp = rnorm(10),
  samp_logical = samp > 0,
  samp_character = c("Monday", "Tusday", "January", "October", "Saturday", "June", "Friday", "April", "March", "Sunday" ),
  samp_levels = factor(c("Fair", "Good", "Good", "Fair", "Excellent", "Fair", "Good", "Excellent", "Fair", "Excellent"))
)
```


#### Calculate the mean of each variable in dataframe
```{r}
#calculate the mean of random size of 10
mean(pull(df, var = 1))

#calculate the mean of logical vector
mean(pull(df, var = 2))

#calculate the mean of character vector
mean(pull(df, var = 3))

#calculate the mean of factor vector
mean(pull(df, var = -1))
```
* The means of numeric vector and logical vector can be calculated. But the means of character vector and factor vector cannot be calculated.


#### Convert the variables from one to another
```{r, eval=FALSE}
#convert the logical vector into numeric vector and calculate mean
logical_numeric = as.numeric(logical_vector)
mean(logical_numeric)

#convert the character vector into numeric vector and calculate mean
character_numeric = as.numeric(character_vector)
mean(character_numeric)

#convert the factor vector into numeric vector and calculate mean
factor_numeric = as.numeric(factor_vector)
mean(factor_numeric)
```
* The logical vector and factor vector can be converted into numeric vectors. For logical vector, TRUE is converted into 1 and False is converted into 0. For factor vector, three different levels of factor are assigned as 1, 2, and 3. After converting, the mean of both vector can be calculated. We can calculate the mean of logical vector without converting into numeric vector since TRUE is considered as 1 and FALSE is considered as 0 automatically. 

* Character vector cannot be converted into numeric vector, which explain why we cannot take the mean of character vector.


## Problem 2

```{r}
# import the data set
data("penguins", package = "palmerpenguins")

# look at the data set
skimr::skim(penguins)

# Calculate mean flipper length
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

Description of data set:
* The data set includes 344 rows and 8 columns. There are 2 factor vectors and 5 numeric vectors. 

* The variables in the data set are:species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. 

* Some values are missing in column of sex, bill_length_mm, bill_depth_mm, flipper_length_mm, and  body_mass_g. 


```{r}
# make a scatter plot
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species), na.rm = TRUE)
```

```{r, eval = FALSE}
# save the plot
ggsave("penguins.pdf")
```